Self Regulation Ontology Retest Data Report

### 2017-11-19 code/SRO_Report.Rmd
Cleaning up report

## Reliability metrics

@@

@@

@@

### Histograms of reliability metrics

```{r warning=FALSE, message=FALSE}
boot_df %>%
  select(dv, task, spearman, pearson, icc) %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(alpha = 0.5, position = 'identity')+
  facet_wrap(~key)+
  theme_bw()+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  xlab("")

ggsave('Booth_Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
```

### Relationship between reliability metrics (point estimates)

Bootstrapped version is essentially the same.

@@

@@

@@

## Variance breakdown

```{r warning=FALSE, message=FALSE}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  # gather(key, value, -dv, -task) %>%
  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
         # var=gsub(".ReflogTr", "", var),
         # var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p1 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  # gather(key, value, -dv, -task) %>%
  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p2 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75)+
  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

```{r}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) 
  # do(tidy(lm(value~key*task, data=.)))

summary(lm(value~key*task,tmp))
```

```{r}
aggregate(value ~task+key, FUN=mean, data=tmp)
```

Summarizing for clearer presentation

What does it look like for DDM variables separately?

```{r warning=FALSE, message=FALSE}
p1_ddm = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) %>%
  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         grepl("EZ|hddm", dv))%>%
  ggplot(aes(x=var, y=value, fill=key))+
  geom_bar(stat='identity', alpha = 0.75)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                     h=c(100,500))+
  ylab("")+
  xlab("")

ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1_ddm, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
```

>>>>

## Relationship between reliability metrics (point estimates)

@@

```{r}
#Create df of point estimate reliabilities
numeric_cols = c()

@@

Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen. Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman). The bootstrapped version is essentially the same but the plots are busier due to more datapoints.

## Summary of all measure reliabilities

@@

## Survey vs Tasks

### Variance breakdown

The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al. (2017), lies in the difference in sources of variance between these measures. This is because reliability is estimated as a ratio of these sources variance to each other. Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance. Thus, measures with high between subjects variance would have high test-retest reliability. Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.

Here we first plot the percentage of variance explained by the three sources of variance for the point estimates of measure reliabilities. The plot only includes raw measures (no DDM parameters) and the measures are ranked by percentage of between subject variability for each task/survey (i.e. the best to worst individual difference measure for each task/survey). Then we compare statistically whether the percentage of variance explained by these sources differ between tasks and surveys.

```{r warning=FALSE, message=FALSE}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p1 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p2 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75)+
  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

```{r}
tmp = boot_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task)

summary(lmer(value~key*task+(1|dv),tmp))
```

```{r}
aggregate(value ~task+key, FUN=mean, data=tmp)

tmp%>%
  group_by(task, key) %>%
  summarise(median = median(value),
            sd = sd(value))
```

Summarizing for clearer presentation. This grap is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.

@@

### Number of trials

@@

#### Trial number dependence intrameasure

The above analysis was looking at the effect of number of trials across tasks. But some tasks might be bad for individual difference measurement regardless of how many trials there are in them whereas for others fewer trials might be yielding a sufficiently reliable measure.

For tasks for which dependent variables are estimated using many trials one can ask: Does the same measure get less reliable if fewer trials are used to estimate its reliability?

This won't make sense for all tasks. For example to estimate a risk aversion parameter you need all trials for Holt and Laury. For Kirby and Bickel you have specific conditions looking at fewer trials. The Cognitive Reflection Task might be more appropriate to analyze each item seaprately. The writing task does not have trial numbers. For all others it might be interesting to investigate.

That said this kind of analysis seems too in the weeds for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time. Such analyses would provide a detailed examination of how to extract the most reliable/best individual difference measure from tasks with a set of mediocre variables to begin with. So I am choosing to ignore this for now but this can be revisited.

### Raw vs DDM

#### DDM Variance breakdown

What does the variance breakdown look like for DDM variables separately?

```{r warning=FALSE, message=FALSE}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         grepl("EZ|hddm", dv))%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p1 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

ggsave('Variance_Breakdown_Plot_DDM.jpg', plot = p1, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 12, height = 20, units = "in")
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot_DDM.jpg')
```

Summarizing it by raw vs fit and for each parameter

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition") %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "var_subs", "var_ind", "var_resid")], by = 'dv') %>%
  mutate(var_subs_pct = (var_subs/(var_subs+var_ind+var_resid))*100,
         var_ind_pct= (var_ind/(var_subs+var_ind+var_resid))*100,
         var_resid_pct = (var_resid/(var_subs+var_ind+var_resid))*100) %>%
  select(-task, -ddm_task, -num_all_trials, -var_subs, -var_ind, -var_resid) %>%
  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)

tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), value, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_grid(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"), labels=c("Variance between subjects", "Variance between individuals", "Error variance"))~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("% of total variance")+
  xlab("")+
  theme(legend.title = element_blank())

ggsave('Variance_Breakdown_Plot_DDM_summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 8, units = "in")
```

Do these differ statistically?

The plot does not suggest so but this model is giving a warning and very high t values. How else should I be checking for differences between these distributions?

```{r}
summary(lmer(value~key*overall_difference*raw_fit+(1|dv), tmp))
```

#### Change in parameter values depending on sample

How much do parameter values change depending on whether the model was fit using the whole sample vs only the retest sample. Each point in these graphs is a subject's parameter estimates. There is almost no change for any of the EZ parameters (though shouldn't this have been 0?). For the HDDM parameters most of the changes are happening for drift rates but they don't appear to be systematically higher or lower.

I'm not entirely sure what to make of this

```{r warning=FALSE, message=FALSE}
hddm_fullfits <- test_data_full_sample_hddm[,names(test_data_full_sample_hddm) %in% names(hddm_refits)]

hddm_fullfits = hddm_fullfits %>%
  gather(dv, value, -sub_id)

hddm_refits %>%
  gather(dv, value, -sub_id) %>%
  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
  rename(fullfit = value.y, refit = value.x) %>%
  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
  filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
  ggplot(aes(fullfit, refit))+
  geom_point(aes(color=rt_acc))+
  facet_wrap(~raw_fit)+
  theme_bw()+
  geom_abline(slope=1, intercept=0)+
  xlab("Fit on full sample")+
  ylab("Fit on retest sample")+
  theme(legend.title = element_blank())
```

```{r message=FALSE}
tmp = hddm_refits %>%
  gather(dv, value, -sub_id) %>%
  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
  rename(fullfit = value.y, refit = value.x) %>%
  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
  filter(rt_acc %in% c("drift rate","non-decision", "threshold"))
```

#### Parameter reliability depending on sample size

```{r}

```

#### Is the H in HDDM important?

```{r}

```

@@

## Transformation effects
